A Documentary History of \\ the Nock Combinator Calculus

### 2025-07-06 mss.tex
Post

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              Manuscript submitted for review.\\
              % {\it Urbit Systems Technical Journal} II:1 (2025):  1–3. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{A History of Nock}
\fancyfoot[LE,RO]{\thepage}

@@

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{1}

@@

While deviations from the trunk line of the Nock family have been propsed at various points,\footnote{Notably, Ax (see pp.~XX–XX, this volume), \textsc{skew}, and \textsc{plan} (see pp.~XX–XX, this volume).} Nock itself has remained the definitional substrate of Urbit since its inception.  It has also been adopted as the primary \textsc{isa} of Nockchain and the NockApp ecosystem.

@@

@@

\printbibliography
\end{document}

>>>>

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
            %   Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} II:1 (2025):  153–188. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{A History of Nock}
\fancyfoot[LE,RO]{\thepage}

@@

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{153}

@@

While deviations from the trunk line of the Nock family have been proposed at various points,\footnote{Notably, Ax (see pp.~XX–XX, this volume), \textsc{skew}, and \textsc{plan} (see pp.~XX–XX, this volume).} Nock itself has remained the definitional substrate of Urbit since its inception.  It has also been adopted as the primary \textsc{isa} of Nockchain and the NockApp ecosystem.

@@

\begin{quote}
A13:  If you don't completely understand your code and the semantics of all the code it depends on, your code is wrong.

A21: Prefer mechanical simplicity to mathematical simplicity.  Often mechanical simplicity and mathematical simplicity go together.

F1: If it's not deterministic, it isn't real.

(\patp{wicdev-wisryt}, Urbit Precepts (2020))
\end{quote}

@@

\selectlanguage{USenglish}
\printbibliography
\end{document}
